Datasheet for Predicting Probability of Participants' Vote of Conservative and Liberty in 2025 Canadian election

### 2024-04-19 paper/Data sheet.qmd
Add files via upload

---
title: "Datasheet for Predicting Probability of Participants' Vote of Conservative and Liberty in 2025 Canadian election"
abstract: "In our study, we use binary logistic regression to analyze voter preferences for Canada's Conservative and Liberal parties based on demographic and socioeconomic factors, adjusting the models with the AIC for optimal predictor selection. The Canadian electoral system elects parliamentarians through a multi-step process where, unless a candidate achieves an outright majority, votes are redistributed from the lowest-ranking candidates until one secures 50%. The Liberal Party plans to increase its refugee quota to 15% of all immigrants and admit 500,000 migrants annually by 2025. The Conservative Party emphasizes economic growth and attracting skilled immigrants. Our hypothesis predicts a likely Conservative victory in the 2025 elections, with the Liberals closely behind, based on trends and electoral mechanics. This analysis uses post-stratification to enhance the representativeness and accuracy of our predictions."
thanks: "Code and data supporting this analysis are available at https://github.com/CSCmaster/Final-Project"
author: "Jingyi Shen"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
link-citations: true
---

# Motivation

>>>>

---
title: "Datasheet for Predicting Probability of Participants' Vote of Conservative and Liberty in 2025 Canadian election"
abstract: "In our study, we use binary logistic regression to analyze voter preferences for Canada's Conservative and Liberal parties based on demographic and socioeconomic factors, adjusting the models with the AIC for optimal predictor selection. The Canadian electoral system elects parliamentarians through a multi-step process where, unless a candidate achieves an outright majority, votes are redistributed from the lowest-ranking candidates until one secures 50%. The Liberal Party plans to increase its refugee quota to 15% of all immigrants and admit 500,000 migrants annually by 2025. The Conservative Party emphasizes economic growth and attracting skilled immigrants. Our hypothesis predicts a likely Conservative victory in the 2025 elections, with the Liberals closely behind, based on trends and electoral mechanics. This analysis uses post-stratification to enhance the representativeness and accuracy of our predictions."
thanks: "Code and data supporting this analysis are available at https://github.com/CSCmaster/Final-Project"
author: "Jingyi Shen"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: reference.bib
link-citations: true
---
The questions of the data sheet is from @gebru2021datasheets

##  Motivation
